FTLR proof cases

### 2018-06-25 fully-abstract-comp/ftlr-proof-cases.tex
compilation issue fixed

  Now show
  \[
    \npair[n-1]{(\Phi_S'.\reg,\Phi_T'.\reg)} \in \lrrg{\trust}(W_R)
  \]
  assuming that neither of the following is the case:
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:move} and $\isLinear{w_2}$ and $r_2 = \pcreg$.
  \item Case \ref{case:ftlr:move-cca-etc:cseal} and $\isLinear{\Phi_S(r_1)}$ and $r_1 = \pcreg$.
  \end{itemize}

@@

TODO
  \item Case \ref{case:ftlr:move-cca-etc:split-normal}:

TODO
  \item Case \ref{case:ftlr:move-cca-etc:split-seal}:

>>>>

  Now show
  \[
    \npair[n-1]{(\Phi_S'.\reg,\Phi_T'.\reg)} \in \lrrg{\trust}(W_R)
  \]
  assuming that neither of the following is the case:
  \begin{itemize}
  \item Case \ref{case:ftlr:move-cca-etc:move} and $\isLinear{w_2}$ and $r_2 = \pcreg$.
  \item Case \ref{case:ftlr:move-cca-etc:cseal} and $\isLinear{\Phi_S(r_1)}$ and
    $r_1 = \pcreg$.
  \item Case \ref{case:ftlr:move-cca-etc:split-normal} and
    $\isLinear{\Phi_S(r_3)}$ and $\pcreg = r_3$.
  \end{itemize}

@@

TODO
  \item Case \ref{case:ftlr:move-cca-etc:split-normal}:
    First we only consider registers $r_1,r_2,r_3$.

    If $\isLinear{(\Phi_S(r_3))}$, then we need to redistribute the ownership
    previously owned by the world used for $r_3$ to $r_1$ and $r_2$.

    From $\npair{(\Phi_S(r_3),\Phi_S(r_3))} \in \lrvg{\trust}(R_R(r_3))$, we get that either $\perm = \noperm$, in which case we can pick the ownership distribution to be the same as before, or $\npair{[\baddr,\eaddr]} \in \readCond{\linear,R_R(r_3)}$.

    In the latter case, we get $S \subseteq \addressable{\linear,R_R(r_3)}$ and $R : S \fun \powerset{R_R(r_3)}$ such that $\forall r \in S \ldotp |R(r)| = 1$ and $\biguplus_{r\in S} R(r) \supseteq [\baddr,\eaddr]$.

    This gives us a way to distribute the ownership, namely $r_3$ gives up ownership of regions $R^{-1}([\baddr,\eaddr])$, $r_1$ gets ownership of $R^{-1}([\baddr,n])$, and $r_2$ gets ownership over $R^{-1}([n+1,\eaddr])$.
    The remainder of the ownership distribution remains unchanged.

TODO TODO TODO     
    Now we have to argue the following:
    \begin{itemize}
    \item if $\perm \in \readAllowed$, then
      \begin{itemize}
      \item $\npair{[\baddr,n]} \in \readCond{\linear,R_R'(r_1)}$
      \item $\npair{[n+1,\eaddr]} \in \readCond{R_R'(r_2)}$
      \end{itemize}

    \item if $\perm \in \writeAllowed$, then
      \begin{itemize}
      \item $\npair{[\baddr,n]} \in \writeCond{\linear,R_R'(r_1)}$
      \item $\npair{[n+1,\eaddr]} \in \writeCond{\linear,R_R'(r_2)}$
      \end{itemize}
    \item $\perm \neq \rx$

      Assuming $\perm = \rx$, then it must have been the case that $\lin = \normal$ contradicting the assumption $\isLinear{(\Phi_S(r_3))}$.

    \end{itemize}
    or
    \begin{itemize}
    \item 
    \end{itemize}
    depending on whether the permission of the capability was $\perm = \noperm$
    or not. In both cases, the result follows immediately by the assumptions.

    If $\neg \isLinear{(\Phi_S(r_3))}$, then we pick $R_R' = R_R$

    For regions $r \neq r_1,r_2,r_3$, we have
    \[
      \npair[n-1]{(\Phi_S'(r), \Phi_T'(r))} \in \lrvg{\trust}(R(r_1))
    \]
    by assumption and Lemma~\ref{lem:downwards-closed}.
  \item Case \ref{case:ftlr:move-cca-etc:split-seal}:
